Appendix B: Code for analysis comparing to historical data

### 2019-06-15 appendix/appendixB.Rmd

```{r}
path <- "../data/appendixB/ramlegacy_v3.0.xlsx"
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets

ramlegacy <- 
  ram$timeseries_values_views %>%
  select(assessid, stockid, stocklong, year, SSB, TC) %>%
  left_join(ram$stock) %>%
  left_join(ram$area) %>%
  select(assessid, stockid, scientificname, 
         commonname, areaname, country, year, 
         SSB, TC) %>%
  left_join(ram$timeseries_units_views %>%
              rename(TC_units = TC, SSB_units = SSB)) %>%
  select(scientificname, commonname, 
         stockid, areaname, country, year, 
         SSB, TC, SSB_units, TC_units)
```

>>>>

```{r}
#if(!file.exists("ramlegacy.zip")){
#download.file(paste0(
#  "https://depts.washington.edu/ramlegac/wordpress/databaseVersions/",
#  "RLSADB_v3.0_(assessment_data_only)_excel.zip"),
#  "ramlegacy.zip")
#}
## Use more robust source
#path <- unzip("ramlegacy.zip")
#sheets <- readxl::excel_sheets(path)
#ram <- lapply(sheets, readxl::read_excel, path = path)
#names(ram) <- sheets
library(ramlegacy)
download_ramlegacy("3.0", overwrite=TRUE, quiet = TRUE)
ram <- load_ramlegacy("3.0")
```

```{r}
ramlegacy <- 
  ram$timeseries_values_views %>%
  select(assessid, stockid, stocklong, year, SSB, TC) %>%
  left_join(ram$stock) %>%
  left_join(ram$area) %>%
  select(assessid, stockid, scientificname, 
         commonname, areaname, country, year, 
         SSB, TC) %>%
  left_join(ram$timeseries_units_views %>%
              rename(TC_units = TC, SSB_units = SSB)) %>%
  select(scientificname, commonname, 
         stockid, areaname, country, year, 
         SSB, TC, SSB_units, TC_units)
```
